---
title: "RMarkdown Example"
author: "Alex Jones"
date: "27/05/2022"
output:
  html_document: default
  word_document: default
---

```{r include=FALSE}
# Link to follow
# https://github.com/alexjonesphd/ukrn_markdown_demo/archive/refs/heads/main.zip

# Loads up the packages
library(tidyverse) # General data manipulation and plotting
library(knitr) # building pretty tables

# Read in the csv of our penguin data
penguins <- read_csv('data/penguins_data.csv')
head(penguins, 5)
```

```{r include=FALSE}
# Work out some basic pieces of information #
# number of total observations 
# number of observations for each species
# number of male/female penguins
# Earliest and latest time points (period of data collection)

# nrow gives the number of rows - this is a single number
total_obs <- nrow(penguins)

# count will give the observations within each species, as a `tibble` which is like a small spreadsheet
species_count <- count(penguins, species)

# Same as above for sex
sex_count <- count(penguins, sex)

# We can find the minimum and maximum year using summarise and the min/max functions, again, as a `tibble`
time_period <- summarise(penguins, starting = min(year), ending = max(year))

# Have a look at these variables
print(total_obs)
print(species_count)
print(sex_count)
print(time_period)

# We're ready to start our first results section line!
```
# Method and Results
#### Penguin Participants
A total of `r total_obs` penguins of three different species were recorded during the `r time_period['starting']` to `r time_period['ending']` period. We observed `r filter(species_count, species == "Gentoo")$n` Gentoo, `r filter(species_count, species == "Adelie")$n` Adelie, and `r filter(species_count, species == "Chinstrap")$n` Chinstrap penguins. There were `r filter(sex_count, sex == "female")$n` females and `r filter(sex_count, sex == "male")$n` males, with sex unclassified for `r filter(sex_count, is.na(sex))$n`. 

```{r include=FALSE}
# Now we want to describe a variable of interest, which is the body mass of the penguins. Its easy to work out the mean and SD of this
body_descriptives <- summarise(penguins, mean_mass = mean(body_mass_g), stddev_mass = sd(body_mass_g))
```

Across all species and both females and males, penguins weighed *M* = `r body_descriptives['mean_mass']`, *SD* = `r body_descriptives['stddev_mass']` grams. 

#### Analysis
To test for dimorphism in each penguin species, we submitted the body mass variable to a 2 (Sex: Female, Male) x 3 (Species: Gentoo, Adelie, Chinstrap) ANOVA. The results of the ANOVA are shown in Table 1. 

```{r echo=FALSE}
# Do the anova
anova_data <- aov(body_mass_g ~ species * sex, data=penguins)

# Get the table of results of the anova
results <- summary(anova_data)[[1]]

# Make it look pretty 
kable(results, caption='Table 1: ANOVA on body mass')
```

To explore the significant interaction, we visually inspected our data (shown in Figure 1) before conducting post-hoc comparisons.

```{r echo=FALSE, fig.dim=c(6, 4), fig.retina=TRUE}
plot_data <- drop_na(penguins) 

plot1 <- ggplot(plot_data, aes(x=species, y=body_mass_g, shape=sex, color=sex)) +
  geom_boxplot(outlier.alpha = 0) + 
  geom_point(position=position_jitterdodge(), alpha=.6) +
  labs(y='Body Mass (g)', x='Species', shape='Sex', color='Sex') +
  scale_color_manual(values=c('black', 'grey')) +
  theme_classic()
  
plot1
```


